Toronto Paramedic Services

### 2024-09-26 paper/paper.qmd
Finalized map and changed colours of graphs.

data |>
  pivot_longer(
    cols = c("Total_Emergency_Calls", "Medical_Emergency_Calls", "Vehicle_Accident_Calls", "Emergency_Transfer_Calls", "Fire_Calls", "Airport_Standby_Calls"),
    names_to = "series",
    values_to = "value"
  ) |>
  ggplot(mapping = aes(x = Year, y = value, colour = series)) +
  geom_line() +
  geom_point() +
  theme_light() +
  labs(
    x = "Year", colour = "Incident Type",
    caption = "Data Source: Toronto Paramedic Services"
  ) +
  scale_colour_brewer(palette = "Set3", labels = c("Airport Standbys", "Emergency Transfers", "Fires", "Medical Emergencies", "Total Emergency Calls", "Vehicle Accidents")) +
  ggtitle("EMS Demand (2017-2022) Based on Incident Type") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(0,300000) + scale_y_continuous(name = "Demand for EMS", labels = scales::comma)
```
```{r}
#| echo: false 
#| message: false
#| label: fig-incidentemsdemandzoom
#| fig-cap: EMS Demand for Each Year between 2017 and 2022

@@

data |>
  pivot_longer(
    cols = c("Vehicle_Accident_Calls", "Emergency_Transfer_Calls", "Fire_Calls", "Airport_Standby_Calls"),
    names_to = "series",
    values_to = "value"
  ) |>
  ggplot(mapping = aes(x = Year, y = value, colour = series)) +
  geom_line() +
  geom_point() +
  theme_light() +
  labs(
    x = "Year", colour = "Incident Type",
    caption = "Data Source: Toronto Paramedic Services"
  ) +
  scale_colour_brewer(palette = "Set3", labels = c("Airport Standbys", "Emergency Transfers", "Fires", "Vehicle Accidents")) +
  ggtitle("EMS Demand (2017-2022) Based on Incident Type") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(0,20000) + scale_y_continuous(name = "Demand for EMS", labels = scales::comma)
```

@@

ggplot(merged_map_data) + 
  geom_sf(aes(fill = "EMS Demand Driver")) +
  labs(title = "EMS Demand Drivers By Forward Sortation Area (FSA)",
         x = "Longitude", y="Latitude", 
       caption = "Data Source: Open Canada 2021 Census - Boundary Files & Toronto Paramedic Services",
       labels = c("Medical Emergencies")) +
  theme_light() + theme(plot.title = element_text(hjust = 0.5))

>>>>

data |>
  pivot_longer(
    cols = c("Total_Emergency_Calls", "Medical_Emergency_Calls", "Vehicle_Accident_Calls", "Emergency_Transfer_Calls", "Fire_Calls", "Airport_Standby_Calls"),
    names_to = "series",
    values_to = "value"
  ) |>
  ggplot(mapping = aes(x = Year, y = value, colour = series)) +
  geom_line() +
  geom_point() +
  theme_light() +
  labs(
    x = "Year", colour = "Incident Type",
    caption = "Data Source: Toronto Paramedic Services"
  ) +
  scale_colour_brewer(palette = "Dark2", labels = c("Airport Standbys", "Emergency Transfers", "Fires", "Medical Emergencies", "Total Emergency Calls", "Vehicle Accidents")) +
  ggtitle("EMS Demand (2017-2022) Based on Incident Type") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(0,300000) + scale_y_continuous(name = "Demand for EMS", labels = scales::comma)
```
```{r}
#| echo: false 
#| message: false
#| label: fig-incidentemsdemandzoom
#| fig-cap: EMS Demand for Each Year between 2017 and 2022

@@

data |>
  pivot_longer(
    cols = c("Vehicle_Accident_Calls", "Emergency_Transfer_Calls", "Fire_Calls", "Airport_Standby_Calls"),
    names_to = "series",
    values_to = "value"
  ) |>
  ggplot(mapping = aes(x = Year, y = value, colour = series)) +
  geom_line() +
  geom_point() +
  theme_light() +
  labs(
    x = "Year", colour = "Incident Type",
    caption = "Data Source: Toronto Paramedic Services"
  ) +
  scale_colour_brewer(palette = "Dark2", labels = c("Airport Standbys", "Emergency Transfers", "Fires", "Vehicle Accidents")) +
  ggtitle("EMS Demand (2017-2022) Based on Incident Type") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ylim(0,20000) + scale_y_continuous(name = "Demand for EMS", labels = scales::comma)
```

@@

ggplot(merged_map_data) + 
  geom_sf(aes(fill = EMS_Demand_Driver)) +
  labs(title = "EMS Demand Drivers By Forward Sortation Area (FSA)",
         x = "Longitude", y="Latitude", 
       caption = "Data Source: Open Canada 2021 Census - Boundary Files & Toronto Paramedic Services") +
  theme_light() + theme(plot.title = element_text(hjust = 0.5)) +
  scale_fill_discrete(name = "EMS Demand Driver") +
  scale_fill_manual(values = c("lightblue"))
